How to Write Theses\\ With Two Line Titles

### 2019-08-25 chapters/methodology/properties.tex
Updates from Overleaf

\section{Identifying Metamorphic Relations} 
We identified seven metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, shifting along-axis, zooming along x-axis, zooming along y-axis. Each image in the testing dataset (digit, letter, and, fashion) was transformed using the seven metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
\subsection{Rotate}
The test images from each dataset is transformed The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle. For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}]. 
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/rotate2.png}
            \caption{Angle: \ang{0}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate3.png}
            \caption{Angle: \ang{50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}
        \caption{Rotation property applied to Digit 3.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shear}  
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\textwidth]{images/shear2.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear3.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

>>>>

\section{Identifying Metamorphic Relations} 
We identified five metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, and, shifting along y-axis. Each image in the testing dataset (digit, letter, and, fashion) was transformed using the five metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
\subsection{Rotate}
The test images from each dataset is transformed The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle. For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}]. 
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/rotate2.png}
            \caption{Angle: \ang{0}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate3.png}
            \caption{Angle: \ang{50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}
        \caption{Rotation property applied to Digit 3.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shear}  
The images were transformed between angle [-50, 50]
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\textwidth]{images/shear2.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear3.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

### 2019-08-25 chapters/results/results.tex
Updates from Overleaf

\section{Effect of transformation on model}
From literature review we postulate that small changes to input image should not affect the prediction model. In this thesis we investigate the effect of the identified metamorphic properties have on the accuracy of model. For each machine learning algorithms generated ten models . For each metamorphic property identified in section X we look how it affects . We calculated the following metrics to evaluate the affect of metamophic relations on deep-learning algorithm. To tackle the non-deterministic nature of training a neural network model, we ran each of the above experiment ten times and calculated average.
\subsection{Overall Accuracy or true positive}
    Accuracy is defined as the number of correct predictions made by the model with respect to the total number of predictions made.
\subsection{Digit-by Accuracy or true positive for each digit}
    We analyze each digit and 
\subsection{Misclassification of digits}
    In order to see how each digit is affected by changes in  mp. For each digit 0-9 we calculated the number of correct predictions made by the model as compared to total number of .
\subsection{Robustness}

@@

>>>>

\section{Effect of transformation on model}
From literature review we postulate that small changes to input image should not affect the prediction model. In this thesis we investigate the effect of the identified metamorphic properties have on the accuracy of model. For each machine learning algorithms generated ten models . For each metamorphic property identified in section X we look how it affects . We calculated the following metrics to evaluate the affect of metamophic relations on deep-learning algorithm. To tackle the non-deterministic nature of training a neural network model, we ran each of the above experiment ten times and calculated average.
\subsection{Overall Accuracy or true positive}
    Accuracy is defined as the number of correct predictions made by the model with respect to the total number of predictions made.
\subsection{Digit-by Accuracy or true positive for each digit}
    We analyze each digit and 
\subsection{Misclassification of digits}
    In order to see how each digit is affected by changes in  mp. For each digit 0-9 we calculated the number of correct predictions made by the model as compared to total number of .
\subsection{Robustness}
We difined robustness in relative terms and we will be comparing the robustness of these algorithms with respect to each other for different datasets and different metamorphic relations. We also attempt to quantify robustness by measuring how tolerant the algorithm is to changes to original input.

@@

We make following recommendations for transforming digits in MNIST dataset.
\import{chapters/results/}{tables.tex}

\newpage
\section{Discussion}
In this paper we identified five metamorphic properties that can be used with image datasets MNIST and MNIST-Fashion. We also provided recommendations for creating follow up test cases from this dataset by providing the most effective values to use for these metamorphic properties. We also evaluated the robustness of five machine learning algorithms on these metamorphic properties.
